\vspace{-2cm} \LARGE Divergence-Free Smoothed Particle Hydrodynamics \\ \large Advanced Simulation and Visualization of Fluids in Computer Graphics

### 2017-01-13 report/paper.tex
Started on sentence for fps
Added specs for frame rate
short conclusion

Since the water aims to be in the state of rest, the motion will decrease over time which is illustrated in Figure~\ref{fig:res3}.
\begin{figure}[h!]
    \includegraphics[width=\linewidth]{img/frame0500.png}
    \caption{caption}
    \label{fig:res3}
\end{figure}

To be able to simulate how outer forces affect the water, we implemented a feature where the user is able to change the direction of the force. The result when applying a force from right to left on the water and then letting only the gravity affect it is shown in Figure~\ref{fig:res4}.
\begin{figure}[h!]
    \includegraphics[width=\linewidth]{img/frame0882.png}
    \caption{caption}
    \label{fig:res4}
\end{figure}

@@

    % Write about FPS when running x amount of particles

@@

>>>>

	Since the water aims to be in the state of rest, the motion will decrease over time which is illustrated in Figure~\ref{fig:res3}.
	\begin{figure}[h!]
		\includegraphics[width=\linewidth]{img/frame0500.png}
		\caption{The water is calm with some motion.}
		\label{fig:res3}
	\end{figure}

	To be able to simulate how outer forces affect the water, we implemented a feature where the user is able to change the direction of the force.
	The result when applying a force from right to left on the water and then letting only the gravity affect it is shown in Figure~\ref{fig:res4}.

	\begin{figure}[h!]
		\includegraphics[width=\linewidth]{img/frame0882.png}
		\caption{The water after an applied right to left motion followed by gravity as the only outer force.}
		\label{fig:res4}
	\end{figure}

@@

    % Write about FPS when running x amount of particles
	When running the program in real time with 5000 particles it runs with a frame rate of 6-8 fps on the MAC computer.
	When instead simulating with $10,000$ particles the frame rate is about 2 fps on the MAC computer.

@@

    % Conclusion
    We were able to implement the SPH method presented by Bender et al.~\cite{bender} which induce that the fluid is incompressible. Though, there are several possible improvements that would improve the implementation and increase the frame rate.
